---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

options(tidyverse.quiet = TRUE)
```

# classCleaner

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of classCleaner is to ...

## Installation

<!-- You can install the released version of classCleaner from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("classCleaner") -->
<!-- ``` -->
`classCleaner` is currently only available on [Github](https://github.com/), where it can be downloaded at
<!-- And the development version from [GitHub](https://github.com/) with: -->

``` r
# install.packages("devtools")
devtools::install_github("melkey/classCleaner")
```
## Example

Here's a simple example of `classCleaner` on the Congressional Voting Records Data Set from the UCI Machine Learning Repository.
Although `classCleaner` does not require any tidyverse package, it's included to clean and present the data.

The data consists of (simplified) voting records for each member of the US House of Representatives on 16 key votes (identified by the CQA) in 1984.
Each Representative's vote is summarized as "y" (voted for), "n" (voted against), and "?" (voted present or did not vote).
We use `classCleaner` to identify which party members tended to vote in a manner different from their political party.

```{r load-data}
library(classCleaner)
library(tidyverse)

## load example data set

votes <- read_csv(
  "https://archive.ics.uci.edu/ml/machine-learning-databases/voting-records/house-votes-84.data",
  col_types = cols(),
  col_names = c('party', paste0("v", 1:16))
) %>%
  print()

```

`ClassCleaner`, requires a matrix of pairwise distances between the Representatives.
To do this, we recode the `v1` - `v16`, with `y -> 1`, `n -> 0`, and `? -> 0.5`, and use Manhattan ("city-block") distance to calculate the distance between Representatives.

```{r recode-vars, warning=FALSE}
votes <- votes %>%
  mutate_at(vars(v1:v16), 
    ~ recode(., 
      'y' = 1,
      'n' = 0,
      '?' = .5
    )
  ) %>%
  print()

dist_mat <- votes %>% 
  as.data.frame(select(., -1)) %>%
  as.matrix() %>%
  dist(method = "manhattan") %>%
  as.matrix()
```

Running classCleaner on this produces
```{r classCleaner}
cc_result <- classCleaner(dist_mat, votes$party)

print(cc_result)
```
